### 2015-07-07 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:07:07	12:34:34	(Tue 7.Jul)

One way to improve the performance of imaging devices is to make them more intelligent. 
To improve the performance of modern imaging devices is becoming increasingly intelligent, they adapt their behaviour to best fit the situation they are in. A regular compact camera for instance, adjusts its shutter opening and speed to

The image quality of any imaging device is mostly its by its hardware components, and . 
\IEEEPARstart{D}{ata-driven} methods have been introduced in various imaging fields over the years in attempts to improve image quality. One such method is the minimum variance distortionless response (MVDR) beamformer. Compared to conventional methods, MVDR is often able to improve image contrast and resolution, as shown in~\cite{Blomberg2013,Blomberg2012a,Dursun2009,Lo2004}.

@@

Variables of interest:
\begin{itemize}
\item Window function. Mostly symmetrical, in particular in shadow and for the most part in speckle. In highlight regions more varying.
\end{itemize}

\begin{table}[!b]\centering%\normalsize
\begin{tabular}[c]{l c c c}\hline
\rowcolor{tabBlue} & \bf Highlight & \bf Shadow & \bf Speckle  \\\hline
Symmetry  & Moderate & High & High \\
Mainlobe  & Varying  & Wide & Narrow \\
Sidelobes & Varying  &  & \\
Steering  &          & 
\end{tabular}
\caption{Summary}\label{tab:summary}
\end{table}%

@@

>>>>

\IEEEPARstart{D}{ata-driven} methods have been introduced in various imaging fields over the years in attempts to improve image quality. One such method is the minimum variance distortionless response (MVDR) beamformer. Compared to conventional methods, MVDR is often able to improve image contrast and resolution, as shown in~\cite{Blomberg2013,Blomberg2012a,Dursun2009,Lo2004}.

@@

Variables of interest:
\begin{itemize}
\item Window function. Mostly symmetrical, in particular in shadow and for the most part in speckle. In highlight regions more varying.
\item Mainlobe width. Wide in shadows, narrow in detailed regions. Adding windows in between these extremal values.
\item Steering. No steering in shadows, slight steering in speckle and no steering in highlight. Steering more than the -3dB width of the window function has no effect.
\item Oversampling. From our observations one should have at least twice the number of beams as channels. Image is more visually pleasing and appears more detailed up to 8M.
\end{itemize}

\begin{table}[!b]\centering%\normalsize
\begin{tabular}[c]{l c c c}\hline
\rowcolor{tabBlue} & \bf Highlight & \bf Shadow & \bf Speckle  \\\hline
Symmetry  & Moderate & High & High \\
Mainlobe  & Narrow   & Wide & Moderate \\
Sidelobes & High     & Low  & Moderate \\
Steering  & 0$^\circ$ to $\theta_{-3dB}$ &  & 
\end{tabular}
\caption{Summary}\label{tab:summary}
\end{table}%

@@

\begin{itemize}
\item Oversampling tests. Both Holmengraa and cross.
\item Mosaic indicating the number of windows needed.
\item 
\end{itemize}

### 2015-07-07 ThesisJo/introduction.tex
la2pdf commit - 2015:07:07	12:34:34	(Tue 7.Jul)

>>>>

One way to improve the performance of imaging devices is to make them more intelligent. 
To improve the performance of modern imaging devices is becoming increasingly intelligent, they adapt their behaviour to best fit the situation they are in. A regular compact camera for instance, adjusts its shutter opening and speed to

The image quality of any imaging device is mostly its by its hardware components, and .
